Methods for Large Scale Learning to Rank

### 2014-04-23 report/Chapters/LTRMethods.tex
werk aan fenchelrank

\section{FenchelRank}
FenchelRank \cite{Lai2013} learning method that addresses the sparse Learning-to-Rank problem, which is the problem of learning a ranking function with only a few non-zero coefficients with respect to the input features. FenchelRank is based on the theory of Fenchel Duality \cite{Rifkin2007} and uses the genetic algorithm framework proposed by Shalev-Shwartz and Singer \cite{Shalev-Shwartz2010}.

@@

The objective function in Equation \ref{eq:pairwise_l1_loss} is not differentiable everywhere because of its $\ell_1$-norm regularisation term.

>>>>

\section{FenchelRank}
FenchelRank \cite{Lai2013} learning method that addresses the sparse Learning-to-Rank problem, which is the problem of learning a ranking function with only a few non-zero coefficients with respect to the input features. FenchelRank is based on the theory of Fenchel Duality \cite{Rifkin2007} and uses the genetic algorithm framework proposed by Shalev-Shwartz and Singer \cite{Shalev-Shwartz2010}.\\

@@

\noindent where $I_{C}(w)$ is a function that is 0 if condition $C$ is satisfied, and $\infty$ otherwise. $m$ is the dimension of the data, $p$ is the number of pairs in set $P$, $K$ is a matrix in $\mathbb{R}^{p \times m}$ that contains pairwise information. The objective function in Equation \ref{eq:pairwise_l1_loss} is not differentiable everywhere because of its $\ell_1$-norm regularisation term.\\
